---
title: "Simple document"
author: "Yijia Wang"
output: 
  github_document #:
    #toc: true
    #toc_float: true #可以滚动
#pdf_document（不能有滚动栏）
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# section 5

This plot shows the distribution of the $X$ （LaTeX 数学格式）

```{r}
library(tidyverse)
set.seed(0)
samp1=tibble(
  num_var=rnorm(n=500,mean=1),
  log_var=num_var>0, #either True or False
  abs_var=abs(num_var),
  
)

ggplot(samp1,aes(x=abs_var))+geom_histogram()
```

The median is `r round(median(pull(samp1,num_var)),2)`.

```{r}
round(median(pull(samp1,num_var)),2)
```

# section 6

# 1st Level Header
## 2nd Level Header
**bold**  or  __bold__
*italic* or _italic_
`code`
superscript^2^ and subscript~2~


# section 7: learning assessment 3

* The median is `r round(median(pull(samp1,num_var)),2)`.
